intRo

### 2016-06-21 presentations/user-2016/index.Rmd
fix bot.ly link

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare <br/> Iowa State University"
date: "June 28, 2016 <br> http://j.mp/intRo-JSM2015"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---

>>>>

---
title: "intRo"
subtitle: "Statistical Analysis Software for Teaching"
author: "Andee Kaplan & Eric Hare <br/> Iowa State University"
date: "June 28, 2016 <br> http://bit.ly/intRo-useR2016"
output: ioslides_presentation
font-family: Helvetica
ioslides_presentation:
    logo: images/icon.png
    widescreen: true
---
